The Conjunctive Disjunctive Graph Node Kernel for Disease Gene Prioritization

### 2017-11-16 neurocomputingv3.tex

\subsection{Model Selection}
The hyper-parameters of the various methods were tuned using a 10-fold cross validation. However, due to the non i.i.d. nature of the problem, we emploied a stronger setup to ensure no information leakage. The dataset $0$ (Connective) on which we  validated the performance was never subsequently used in the predictive performance estimation. The values for the diffusion parameter $\beta$ in LEDK and MEDK were sampled in $\lbrace 10^{-3}, 10^{-3}, 10^{-2}, 10^{-1} \rbrace$, time steps $t$ in MDK in $\lbrace 1, 10, 100 \rbrace$ and RLK parameter $\beta$ in $\lbrace 1, 4, 7 \rbrace$. For CDNK, the degree threshold values, $D$, were sampled in $\lbrace 10,\ 15,\ 20 \rbrace$, clique size threshold, $C$, in $\lbrace 4,\ 5 \rbrace$, maximum radius, $r^*$, in $\lbrace 1,\ 2 \rbrace$, maximum distance, $d^*$, in $\lbrace 1, 2,\ 3,\ 4 \rbrace$, number of clusters $P$ in $\lbrace 5,\ 7 \rbrace$. Finally, the regularization trade off parameter in the SVM was sampled in $\lbrace 10^{-5},  \ 10^{-4}, \ 10^{-3},\ 10^{-2},\ 10^{-1}, 1,\ 10,\ 10^2 \rbrace$. The optimal parameter values of CDNK obtained by validation process are $D = 10$, $C=5$, $r^*=2$, $d^*=1$, $P=15$ and the trade-off parameter of SVM is $10^{-2}$.
%\subsection{Parameter Impact}
%In order to evaluate the stability of kernel w.r.t the change of each parameter values, we perform experiments with disease-gene association 2 on the BioGPS network. For each parameter, first we fix the values of all other parameters, but allow the value of considered papameter to be changed. More precisely, we use the optimal tuple $C = 5,\ d^* = 1,\ D = 20,\ P = 15$ for the fixed of parameters' values. We let the changes of $C$ in $\lbrace 4,\ 5,\ 6,\ 7,\ 8,\ 9\rbrace$, $d^*$ in $\lbrace 1,\ 2,\ 3,\ 4\rbrace$, $D$ in $\lbrace 8,\ 10,\  15,\ 20,\ 30,\ 40,\ 50\rbrace$ and real vector size, $P$ in $\lbrace 8,\ 10,\ 15,\ 20,\ 30,\ 50,\ 70, 90\rbrace$.

\subsection{Results and Discussion}
%==================================================
%==================================================
%==================================================
\begin{table}[h]
\caption{Predictive performance on 11 gene-disease associations in percentage using network induced by the BioGPS. Best results in bold. We report the AUC ROC and after the ``/'' the rank for each kernel method (DK = LEDK; MD = MDK; MED = MEDK; RL = RLK; CDNK1 = ontology for discrete labels; CDNK2 = ontology for both discrete and vector labels; CDNK3 = uniform discrete labels;  CDNK4 = uniform discrete labels and ontology for vector labels.) The last two rows report the averages of AUC ROC and rank over the $11$ diseases.} \vspace{1em}
%\vspace*{5pt}
\centering
\setlength{\tabcolsep}{1mm}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
         & \multicolumn{8}{c|}{\textbf{BioGPS}}\\
 \hline
Disease & DK & MD & MED & RL & CDNK1 & CDNK2 & CDNK3 & CDNK4\\

@@

$\overline{Rank}$ & 6.09 & 7.09 &  5.36 & 4.82 & 4.45 & \textbf{1.64} & 4.18 & 2.27 \\
 \hline 
\end{tabular}
\label{tab:cdnk-biogps}
\end{table}
%=====================================
%=====================================
\begin{table}[h]
\caption{Predictive performance on 11 gene-disease associations in percentage using network induced by the Pathways. Best results in bold. We report the AUC ROC and after the ``/'' the rank for each kernel method (DK = LEDK; MD = MDK; MED = MEDK; RL = RLK; CDNK1 = ontology for discrete labels; CDNK2 = ontology for both discrete and vector labels; CDNK3 = uniform discrete labels;  CDNK4 = uniform discrete labels and ontology for vector labels.) The last two rows report the averages of AUC ROC and rank over the $11$ diseases.} \vspace{1em}
%\vspace*{5pt}
\centering
\setlength{\tabcolsep}{1mm}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
         & \multicolumn{8}{c|}{\textbf{Pathways}} \\
 \hline
Disease & DK & MD & MED & RL & CDNK1 & CDNK2 & CDNK3 & CDNK4 \\

@@

%==================================================
\begin{figure}[h]
\centering
\subfloat[Subfigure 2 list of figures text][]{
\includegraphics[width=0.4\textwidth]{cliques.png}
\label{fig:subfig1}}
\subfloat[Subfigure 3 list of figures text][]{
\includegraphics[width=0.4\textwidth]{distance.png}
\label{fig:subfig2}}
\qquad
\subfloat[Subfigure 2 list of figures text][]{
\includegraphics[width=0.4\textwidth]{degree.png}
\label{fig:subfig3}}
\subfloat[Subfigure 3 list of figures text][]{
\includegraphics[width=0.4\textwidth]{vec_size.png}
\label{fig:subfig4}}
\caption{\label{fig:globfig} Performance of CDNK4 on the BioGPS network for disease 2 (Dermatological) w.r.t the change of most of the hyper-parameters: (a) clique threshold ($C$); (b) distance threshold ($d^*$); (c) degree threshold ($D$); (d) real vec size threshold ($P$). The radius ($r^*$) was not changed because of computational reasons.}
\end{figure}

>>>>

\subsection{Model Selection}
The hyper-parameters of the various methods were tuned using a 10-fold cross validation. However, due to the non i.i.d. nature of the problem, we emploied a stronger setup to ensure no information leakage. The dataset $0$ (Connective) on which we  validated the performance was never subsequently used in the predictive performance estimation. The values for the diffusion parameter $\beta$ in LEDK and MEDK were sampled in $\lbrace 10^{-3}, 10^{-3}, 10^{-2}, 10^{-1} \rbrace$, time steps $t$ in MDK in $\lbrace 1, 10, 100 \rbrace$ and RLK parameter $\beta$ in $\lbrace 1, 4, 7 \rbrace$. For CDNK, the degree threshold values, $D$, were sampled in $\lbrace 10,\ 15,\ 20 \rbrace$, clique size threshold, $C$, in $\lbrace 4,\ 5 \rbrace$, maximum radius, $r^*$, in $\lbrace 1,\ 2 \rbrace$, maximum distance, $d^*$, in $\lbrace 1, 2,\ 3,\ 4 \rbrace$, number of clusters $P$ in $\lbrace 5,\ 7 \rbrace$. Finally, the regularization trade off parameter in the SVM was sampled in $\lbrace 10^{-5},  \ 10^{-4}, \ 10^{-3},\ 10^{-2},\ 10^{-1}, 1,\ 10,\ 10^2 \rbrace$. The optimal parameter values of CDNK obtained by validation process are $D = 20$, $C=5$, $r^*=2$, $d^*=1$, $P=15$ and the trade-off parameter of SVM is $10^{-2}$.

%\subsection{Parameter Impact}
%In order to evaluate the stability of kernel w.r.t the change of each parameter values, we perform experiments with disease-gene association 2 on the BioGPS network. For each parameter, first we fix the values of all other parameters, but allow the value of considered papameter to be changed. More precisely, we use the optimal tuple $C = 5,\ d^* = 1,\ D = 20,\ P = 15$ for the fixed of parameters' values. We let the changes of $C$ in $\lbrace 4,\ 5,\ 6,\ 7,\ 8,\ 9\rbrace$, $d^*$ in $\lbrace 1,\ 2,\ 3,\ 4\rbrace$, $D$ in $\lbrace 8,\ 10,\  15,\ 20,\ 30,\ 40,\ 50\rbrace$ and real vector size, $P$ in $\lbrace 8,\ 10,\ 15,\ 20,\ 30,\ 50,\ 70, 90\rbrace$.

\subsection{Results and Discussion}

\begin{table}[h]
\caption{Predictive performance on 11 gene-disease associations in percentage using network induced by the BioGPS. Best results in bold. We report the AUC ROC and after the ``/'' the rank for each kernel method (DK = LEDK; MD = MDK; MED = MEDK; RL = RLK; CDNK1 = ontology for discrete labels; CDNK2 = ontology for both discrete and vector labels; CDNK3 = uniform discrete labels;  CDNK4 = uniform discrete labels and ontology for vector labels.) The last two rows report the averages of AUC ROC and rank over the $11$ diseases.} \vspace{1em}
%\vspace*{5pt}
\centering
\setlength{\tabcolsep}{1mm}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
         & \multicolumn{8}{c|}{\textbf{BioGPS}}\\
 \hline
Disease & DK & MD & MED & RL & CDNK1 & CDNK2 & CDNK3 & CDNK4\\

@@

$\overline{Rank}$ & 6.09 & 7.09 &  5.36 & 4.82 & 4.45 & \textbf{1.64} & 4.18 & 2.27 \\
 \hline 
\end{tabular}
\label{tab:cdnk-biogps}
\end{table}

\begin{table}[h]
\caption{Predictive performance on 11 gene-disease associations in percentage using network induced by the Pathways. Best results in bold. We report the AUC ROC and after the ``/'' the rank for each kernel method (DK = LEDK; MD = MDK; MED = MEDK; RL = RLK; CDNK1 = ontology for discrete labels; CDNK2 = ontology for both discrete and vector labels; CDNK3 = uniform discrete labels;  CDNK4 = uniform discrete labels and ontology for vector labels.) The last two rows report the averages of AUC ROC and rank over the $11$ diseases.} \vspace{1em}
%\vspace*{5pt}
\centering
\setlength{\tabcolsep}{1mm}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
\hline
         & \multicolumn{8}{c|}{\textbf{Pathways}} \\
 \hline
Disease & DK & MD & MED & RL & CDNK1 & CDNK2 & CDNK3 & CDNK4 \\

@@

\begin{figure}[h]
\centering
\subfloat[Subfigure 2 list of figures text][]{
\includegraphics[width=0.4\textwidth]{cliques.png}
\label{fig:subfig1}}
\subfloat[Subfigure 3 list of figures text][]{
\includegraphics[width=0.4\textwidth]{distance.png}
\label{fig:subfig2}}
\qquad
\subfloat[Subfigure 2 list of figures text][]{
\includegraphics[width=0.4\textwidth]{degree.png}
\label{fig:subfig3}}
\subfloat[Subfigure 3 list of figures text][]{
\includegraphics[width=0.4\textwidth]{vec_size.png}
\label{fig:subfig4}}
\caption{\label{fig:globfig} Performance of CDNK4 on the BioGPS network for disease 2 (Dermatological) w.r.t the change of most of the hyper-parameters: (a) clique threshold ($C$); (b) distance threshold ($d^*$); (c) degree threshold ($D$); (d) real vec size threshold ($P$). The radius ($r^*$) was not changed because of computational reasons.}
\end{figure}
